\documentclass[a4paper,12pt, final]{book}

\usepackage{titlesec}
\usepackage{verbatim}

\usepackage[cm-default]{fontspec}


 %\XeTeXtracingfonts=1 

%\newfontfamily\unicodefont{Oxygen}
\defaultfontfeatures{Scale=MatchLowercase,Mapping=tex-text}
\setmainfont[ExternalLocation=./fonts/]{Nunito-Light.ttf}
%\setmainfont{Oxygen}
%\setromanfont{Oxygen}
%\setsansfont{Oxygen}
\setmonofont[ExternalLocation=./fonts/]{Nunito-Regular.ttf}

\usepackage{xunicode}
\usepackage{xltxtra}
\usepackage{calc}
\usepackage{array}
\usepackage{color}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{shorttoc}
\usepackage{graphicx}
%\usepackage{natbib}
\usepackage{german, hyperref} 
\usepackage{makeidx}
\usepackage[style=alphabetic-verb]{biblatex}


%\bibliography{imagequality}

\graphicspath{{images/}}

\renewcommand{\labelitemi}{$\cdot$}



\frontmatter
\pagestyle{fancy}      
\fancyhead[RO, LE]{\fontfamily{phv}\selectfont \rightmark}
\fancyhead[RE, LO]{\fontfamily{phv}\selectfont \thepage}
\fancyhead[CE, CO]{}
\fancyfoot[CE, CO]{}

 \makeatletter
 \makeindex
 
\def\cleardoublepage{\vspace{1.0cm}}  
\def\clearpage{\vspace{1.0cm}}
%\def\newpage{\vspace{1.0cm}}
\makeatother        
 

\titleformat{\section}%
  {\Large\bfseries \filcenter}%
  {\thesection}%
  {1em}%
  {}%


\titleformat{\subsection}%
  {\large\bfseries \filcenter}%
  {\thesubsection}%
  {1em}%
  {}%


\titleformat{\subsubsection}%
  {\normalsize\bfseries \filcenter}%
  {\thesubsection}%
  {1em}%
  {}%


\titleformat{\chapter}%
  {\huge\bfseries \filcenter}%
  {\thechapter}%
  {1em}%
  {}%

\titleformat{\part}%`
  { \Huge\bfseries \filcenter}%
  {\thepart}%
  {1em}%
  {}%


\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}

\newenvironment{proof}[1][Proof]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{definition}[1][Definition]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{example}[1][Example]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{remark}[1][Remark]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}

\newenvironment{code}{\small\verbatim}{\endverbatim}



\newcommand{\qed}{\nobreak \ifvmode \relax \else
      \ifdim\lastskip<1.5em \hskip-\lastskip
      \hskip1.5em plus0em minus0.5em \fi \nobreak
      \vrule height0.75em width0.5em depth0.25em\fi}

\def\lra{\longrightarrow}


\newcommand{\mnote}[1]{\marginpar{%
	\vskip-\baselineskip
	\raggedright\footnotesize
	\itshape\hrule\smallskip\tiny{#1}\par\smallskip\hrule}}

\mainmatter

\begin{document}

\pagestyle{empty}
{\center

{\Huge
SharkSVM manual v0.1
}\vfil}
 
\newpage
 

\tableofcontents

\newpage 


\chapter{Introduction}


\section{What is SharkSVM?}

SharkSVM is a command line wrapper for the 
high-performance C++ machine learning library Shark.
As an open source project SharkSVM can harrness
the inherent power of the community.

Why is SharkSVM a good choice?

\begin{itemize}
\item It contains highly optimized code.
\end{itemize}

As an open source project, we can use the all the power of the
open source world:



\section{Features}

SharkSVM supports the algorithms
\begin{itemize}
  \item SMO
  \item BSGD
  \item RFF
  \item ICF
\end{itemize}



\section{ToDos and Ideas}

\begin{itemize}
\item json?
\end{itemize}


\section{The other side of the coin}

Though we will take some care not to include patented algorithms,
we cannot take any guarantees that by using this software, you are
making use of third-party patents.
If you see anything that infringes any patent or copyright, please
tell us, we will remove the offending parts immediately and will
try to find another workaround.



 
\chapter{Using SharkSVM}


\section{Simple example}



\chapter{Tickets}






\section{Input Data}

Datasets can be read in the wide-spread Sparse Data format.
Alternatively there are some converters.


\section{Output}

The output is a modified LIBSVM model.


\section{Logs}

format of log (=HTML, XML, JSON?, TXT), place for log, filename for log.



\chapter{Technical side}



\section{Unittests}

or whitebox testing.


\section{Sourcecode Structure}

In case you want to help us by either fixing bugs or
developing new features, here are some guidelines.


\chapter{Appendix}



\section{Licences}

SharkSVM is LGPL. Shark is LGPL.
Boost is Boost.

Document created with XeLateX.

This document uses the Nunito font.


\printindex

\end{document}
